\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage[utf8]{inputenc}
\usepackage[english, russian]{babel}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\moderncvstyle{casual}
\moderncvcolor{burgundy}

\usepackage[scale=0.75]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}

\firstname{Natalia}
\familyname{Ponomareva}

\phone{+7~(921)~973-26-89}
\email{natpon12@gmail.com}
%\photo[100pt]{photo.jpg}
\nopagenumbers{}

\begin{document}
\makecvtitle

\section{Education}
\cventry{2013 -- 2016}{Student}{30 Phys-Math Lyceum}{}{}{}
\cventry{2018 -- 2019}{Student}{Computer Science Center}{}{}{}
\cventry{2016 -- 2020}{Bachelor's degree in Mathematics and Mechanics, educational program ``Software and Administration of Information Systems''}{Saint Petersburg State University}{}{GPA: 4.9/5}{}
\section{Work experience}
\cventry{Summer 2018}{Intern C\# Developer}{Arcadia Software Country}{}{}{}
\cventry{2020-2022}{Java Developer}{Deutsche Bank Technology Center}{}{}{Development of investment products for liquidity management:
	\begin{itemize}
		\item analyzed and designed program changes, interacted with other teams and business leads to deliver completed features,
		\item applied relevant technical skills to deliver specifications, program changes, unit test scripts and documentation,
		\item supported application, interacted with end users, fixed bugs
	\end{itemize}
}

\section{Projects and Achievements}
\cventry{2014-2015}{Computer graphics course at school}{Participation in conferences, experience in representing and defending own project}{}{}{}
\cventry{2017}{Dell Emc scholarship}{Successful completion of the first year of university}{}{}{}
\cventry{2019}{Coursework, Multi-view reconstruction of a dense point cloud with image segmentation}{}{}{}{}
\cventry{2020}{Diploma, Real-time non-rigid reconstruction of human bodies from RGB-D video sequences}{}{}{}{}

\section{Skills and professional interests}
\cvitem{Programming}{Strong overall programming skills. Firm understanding of design and analysis of algorithms. Language of choice is Java, basic knowledge of C++/Objective C, Python, C\#, Haskell, asm.}
\cvitem{Frameworks}{Spring, Docker, REST, Oracle SQL.}
\cvitem{Mathematics}{Strong mathematical background. Firm knowledge in fundamental fields (abstract algebra, real analysis, probability theory). Basic understanding of numerical methods.}
\cvitem{Infrastructure}{Confident user of Unix, Git, LaTeX, Jira.}
\cvitem{Languages}{Russian (native), English (fluent)}{}

\end{document}